\textit{Urban and building multiscale co-simulation: case study implementations on two university campuses}

### 2017-07-07 thirdsubmission/6_ThirdSubmission_SourceFile.tex
Made second revision changes

\author{Clayton Miller\textsuperscript{a,b}%
$^{\ast}$\thanks{$^\ast$Corresponding author. Email: clayton@nus.edu.sg}, 
Daren Thomas\textsuperscript{a},
J\'er\^ome K\"ampf\textsuperscript{c},
and Arno Schlueter\textsuperscript{a}\\
\vspace{6pt}
\textsuperscript{a}{\em Architecture and Building Systems (A/S), Institute of Technology in Architecture (ITA), ETH Z\"urich, Z\"urich, Switzerland};\\
\textsuperscript{b}{\em Department of Building, School of Design and Environment, National University of Singapore, 117566 Singapore};\\
\textsuperscript{c}{\em ENERGY Institute, HEIA-FR / HES-SO Fribourg, Bd Perolles 80, 1750 Fribourg, Switzerland}
}

@@

\subsection{Acknowledgments}
The authors would like to acknowledge the ETH Z\"urich Campus Facilities
Department, the EPFL Real Estate and Infrastructure Department, and Emanuel
Thoma for their assistance in this project. This research was funded by the
Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale
Energy Modeling (UMEM) project.

>>>>

% \author{Clayton Miller\textsuperscript{a,b}%
% $^{\ast}$\thanks{$^\ast$Corresponding author. Email: clayton@nus.edu.sg}, 
% Daren Thomas\textsuperscript{a},
% J\'er\^ome K\"ampf\textsuperscript{c},
% and Arno Schlueter\textsuperscript{a}\\
% \vspace{6pt}
% \textsuperscript{a}{\em Architecture and Building Systems (A/S), Institute of Technology in Architecture (ITA), ETH Z\"urich, Z\"urich, Switzerland};\\
% \textsuperscript{b}{\em Department of Building, School of Design and Environment, National University of Singapore, 117566 Singapore};\\
% \textsuperscript{c}{\em ENERGY Institute, HEIA-FR / HES-SO Fribourg, Bd Perolles 80, 1750 Fribourg, Switzerland}
% }

@@

% \subsection{Acknowledgments}
% The authors would like to acknowledge the ETH Z\"urich Campus Facilities
% Department, the EPFL Real Estate and Infrastructure Department, and Emanuel
% Thoma for their assistance in this project. This research was funded by the
% Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale
% Energy Modeling (UMEM) project.
